Tables/Graphs for Article

### 2018-01-08 article/draft1.Rnw
edited related works

With the recent increase in the popularity and use of CQAs, these platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model to estimate response times for questions posted on \textit{Stack Overflow} using features of the questions. Analysis determined that tag-based features, like the number of ``popular'' tags a question contains or the number of users subscribed to a tag, were the best predictors. \cite{Mahmud2013} approached response time analysis with a different method, and proposed models to predict response times of questions posted on Twitter based on exponential distributions and built from users' previous wait times for responses. In contrast, \cite{Asaduzzaman2013} focused exclusively on unanswered questions and developed a taxonomy for classifying such questions on \textit{Stack Overflow}, and created a model to predict how long a question would remain unanswered using both textual features of the questions and characteristics of the user. All research mentioned restricted analysis to either questions for which response times were observed, or to questions that remained unanswered. The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

The majority of existing research has been focused on predicting question and answer quality by using both textual and non-textual features of posts. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com}, using primarily textual features of the questions. \cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate metric of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). On the other hand, \cite{H.fu} found that non-textual features, like revision and comment count on an answer or the number of points or merit badges a user has, were the most useful indicators of answer quality across four different knowledge domains on \textit{Stack Exchange}. A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a} \cite{Ravi2014}. All research previously mentioned restricted analysis to predicting either question quality or answer quality. \cite{Anderson2012} presented models to predict the long term value or quality of questions as well as its answers on \textit{Stack Overflow}. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors indicating high quality questions also lead to faster response times. (fix this section)

>>>>

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions on \textit{Stack Overflow}, and created a model to predict how long a question would remain unanswered. All research mentioned restricted analysis to either questions for which response times were observed, or to questions that remained unanswered. The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

The majority of existing research has been focused on predicting question and answer quality. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions. \cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). \cite{H.fu} instead found that non-textual features, like revision and comment count on an answer or the number of points a user has, were the most useful indicators of answer quality. A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a} \cite{Ravi2014}. \cite{Anderson} took analysis further and presented models to predict the long term value of questions as well as the answers it receives. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors indicating that a question is of high quality, can also lead to faster response times. (fix this section)
